Technique for \earlywarning\ filtering for compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-29 results.tex
red flag pass
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1200 ccdd05d5-56c1-461a-bf98-85f6876523b4

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim$$10^8$
\flops\ to cover a sub-bank comprising $\sim$$10^2$ out of the total $\sim$$10^5$
mass pairs.  Given that modern (ca. 2011) workstations can sustain computation
rates up to $\sim$$10^{10}$ \flops{}, and assuming that other regions of the
parameter space have similar computational scaling, an entire search could be
implemented with $\gtrsim$$10$ machines.  Template length does vary
over the parameter space; lower-mass templates are longer and would require
more computation to analyze while higher-mass templates are shorter and would
require less. However, we consider the estimates based on this sub-bank to be a
reasonable representation.

>>>>

Table~\ref{table:flops} shows that the \lloid\ method requires $\sim$$10^8$
\flops\ to cover a sub-bank comprising $\sim$$10^2$ out of the total $\sim$$10^5$
mass pairs.  Given that modern (ca. 2011) workstations can sustain computation
rates up to $\sim$$10^{10}$ \flops{}, and assuming that other regions of the
parameter space have similar computational scaling, an entire single detector
search could be implemented with $\gtrsim$$10$ machines.  Template length does
vary over the parameter space; lower-mass templates are longer and would
require more computation to analyze while higher-mass templates are shorter and
would require less. However, we consider the estimates based on this sub-bank
to be a reasonable representation.
